\vspace{-1in} Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A Guide for International Students

### 2023-09-18 demystify.tex
update

\begin{enumerate}
    \item \textbf{Cheating}: Cheating, e.g., exams, coding, is a big no-no in the US.  If you're caught cheating, you will face very heavy consequence and likely be expelled from the university (e.g., after the second time).   This is very different from many international countries where cheating is common and often tolerated.  Faculty is extremely good at detecting cheating (how would we not?  we have deal with these situations so many times over so many years), and \emph{will} report cheating cases.  In short, whatever you do, don't cheat---not worth it.
    \item \textbf{Illegal Software}: Using illegal/cracked software is very common in many countries. But do not use/install them on university computer (e.g., computers given by your department or advisor).  It is unlikely that the university will track you down, but it is the \textbf{software company} that will.  They have very sophisticated tools to detect illegal software and will sue your university/department (imagine your department or advisor being sued for half a million dollars, and it is you who caused it).   If you need software, ask your advisor or the department.
\end{enumerate}

>>>>

\begin{enumerate}
    \item \textbf{Cheating}: Cheating, e.g., exams, coding, is a big no-no in the US.  If you're caught cheating, you will face very heavy consequence and likely be expelled from the university (e.g., after the second time at GMU).   This is very different from many international countries where cheating is common and often tolerated.  Faculty is extremely good at detecting cheating (how can we not? we deal with these situations so many times over so many years), and \emph{will} report cheating cases.  In short, whatever you do, don't cheat---not worth it.

    \item \textbf{Illegal Software}: Using illegal/cracked software is very common in many countries. But do not use/install them on university computer (e.g., computers given by your department or advisor).  It is unlikely that the university will track you down, but it is the \textbf{software company} that will.  They have very sophisticated tools to detect illegal software and will sue your university/department.  Imagine your department or advisor being sued for half a million dollars, and it is you who caused it.   If you need software, ask your advisor or the department.
\end{enumerate}
